### 2016-08-26 Chapters/PaperSummary.tex
Update notations

When coupled with \emph{open-source} licensing, modularity is a proper
step towards ensuring reproducibility of results from scientific
simulation software \cite{Gezelter2015}.
Open-source development can fully leverage the benefits
of widespread, cloud-based, free, code development services, such as
hosted distributed version control systems (DVCSs), continuous integration, code
coverage, static and dynamic code analyses, nightly regression testing,
public issue tracking, code review and so forth:
adoption of a modern code development workflow is easily within reach.

>>>>

When coupled with \emph{open-source} licensing, modularity is a proper
step towards ensuring reproducibility of results from scientific
simulation software \cite{Gezelter2015-gz, Krylov2015-fs, Jacob2016-oq}.
Open-source development can fully leverage the benefits
of widespread, cloud-based, free, code development services, such as
hosted distributed version control systems (DVCSs), continuous integration, code
coverage, static and dynamic code analyses, nightly regression testing,
public issue tracking, code review and so forth:
adoption of a modern code development workflow is easily within reach.

### 2016-08-26 FrontBackmatter/Notation.tex
Update notations

A number of notations and typographic conventions has been adopted in
order to maintain consistency throughout. We summarize them here:
\begin{table*}[!h]
\begin{tabular}{c l}
 $\bi{A}, \bi{D}, \ldots$ & integral operators over a closed subset of $\mathbb{R}^2$ \\
 $H, \varPhi, \ldots$ & first or second quantized $N$-electron operators \\
 $\vect{r}, \vect{r}^\prime, \ldots$ & position vectors in $\mathbb{R}^3$ \\
 $\vect{s}, \vect{s}^\prime, \ldots$ & position vectors on a closed surface \\
 $\vect{v}, \vect{q}, \ldots$ & vectors in an arbitrary vector space \\
 $\mat{K}, \mat{F}, \ldots$ & matrices in an arbitrary vector space \\
 $0_N, I_N$ & the zero and the identity in an $N$-dimensional vector space
\end{tabular}
\end{table*}

>>>>

A number of notations and typographic conventions has been adopted in
order to maintain consistency throughout. We summarize them here:

\section*{Basic Notation}
\begin{table*}[!h]
\begin{tabular}{l l}
  $u_E$ & Restriction (trace) of the function $u$ to the set $E$ \\
  $\Span{\vect{v}_1, \ldots, \vect{v}_n}$ & Vector space spanned by the
  vectors $\vect{v}_1, \ldots, \vect{v}_n$ \\
  $\delta_{ij}$ & Kronecker symbol: $\delta_{ij}=1i$ if $i=j$ and 0
  otherwise
\end{tabular}
\end{table*}

\section*{Vectors and Matrices}
\begin{tabular}{l l}
 $\vect{v}, \vect{q}$ & Vectors \\
 $\mat{K}, \mat{F}$ & Matrices \\
 $\mathbb{R}^{m, n}$ & Vector space of real-valued $m\times n$ matrices
 \\
 $\Tr\mat{A}$ & Trace of $\mat{A}$. For $\mat{A}\in\mathbb{R}^{n, n}$,
 $\Tr\mat{A}=\sum_{i=1}^n A_{ii}$ \\
 $0_N, I_N$ & the zero and the identity in an $N$-dimensional vector space
\end{tabular}

\section*{Operators}
\begin{tabular}{c l}
 $\bi{A}, \bi{D}$ & integral operators \\
 $H, \varPhi$ & first or second quantized $N$-electron operators
\end{tabular}

\section*{Function Spaces}
\begin{tabular}{c l}
 $\norm{u}{X}$ & Norm of $u$ in the normed space $X$ \\
 $\mathcal{C}^0(\Omega)$ & Space of continuous
 functions on $\Omega\subset\mathbb{R}^d$ \\
 $\mathcal{C}^k(\Omega)$ & Space of $k$ times
 continuously differentiable functions on $\Omega$ \\
 $L^p(\Omega)$ & Space of functions whose $p$-th power is Lebesgue
 integrable on $\Omega$ \\
 $\norm{u}{0, p, \Omega}$ & Norm in $L^p(\Omega)$: $\norm{u}{0, p,
 \Omega} = (\int_\Omega\diff\vect{r} |u(\vect{r})|^p)^\frac{1}{p}$ \\
 $\norm{u}{\Omega}$ & Norm in $L^2(\Omega)$:
 $\norm{u}{\Omega} = \norm{u}{0, 2,\Omega} = \sqrt{\int_\Omega\diff\vect{r} |u(\vect{r})|^2}$ \\
 $H^s(\Omega)$ & Sobolev space of order $s$ of functions whose
 derivative up to order $s$ are in $L^2(\Omega)$ \\
 $H_0^s(\Omega)$ & Space of functions in $H^2(\Omega)$ with null trace on the boundary of $\Omega$ \\
 $|u|_{s, \Omega}$ & Seminorm in $H^s(\Omega)$:
 $|u|_{s, \Omega} \coloneq \sum_{|\alpha|=s}\norm{\partial^\alpha u}{\Omega}$ \\
 $\norm{u}{s, \Omega}$ & Norm in $H^s(\Omega)$:
 $\norm{u}{s, \Omega} \coloneq \sum_{l \leq s} |u|_{l, \Omega}$
\end{tabular}
